\songsection{Bring It On Home To Me \hfill \normalfont Sam Cooke}
\noindent\rule{\columnwidth}{1pt}
\begin{lstsong}
Intro: | C G7 | F G | C F  | C G |

Verse 1:
       C                  G7
If you ever   change your mind
      C         C7            F
about leaving, leaving me behind
        C               G7               F
Baby, bring it to me, bring your sweet lovin',
G7                  C          F             C          G7
bring it on home to me..yeah, (yeah) yeah, (yeah) yeah. (yeah)

Verse 2:
          C                G7
I know I laughed when you left
          C      C7            F
but now I know I only hurt myself
Baby, bring it to me, bring your sweet lovin'
bring it on home to me..yeah, (yeah) yeah, (yeah) yeah. (yeah)

Verse 3:
G7            C                 G7
I'll give you jewelry and money too
            C         C7             F
that ain't all, honey all I'd do for you
If you'd bring it to me, bring your sweet lovin'
bring it on home to me..yeah, (yeah) yeah, (yeah) yeah. (yeah)

Verse 4:
G7            C               G7
You know I'll always, be your slave
         C       C7           F
til I'm buried, buried in my grave.
Oh, honey, bring it to me, bring your sweet lovin'..
bring it on home to me..yeah, (yeah) yeah, (yeah) yeah. (yeah)

Verse 5:
  C                G7
I try to treat you right,
         C           C7             F               F7
but you stayed out, stayed out til night..but I forgive you.
Bring it to me, bring your sweet lovin'..
bring it on home to me..yeah, (yeah) yeah, (yeah) yeah. (yeah)

Outro:
        C          F             C     G7
yeah, (yeah) yeah, (yeah) yeah. (yeah) yeah,
       C             F             C          G7
(yeah) yeah, (yeah) yeah. (yeah) (yeah) yeah
\end{lstsong}
\newpage
