\songsection{If Love Is A Red Dress \hfill \normalfont Maria McKee}
\noindent\rule{\columnwidth}{1pt}

\begin{multicols}{2}
\begin{lstsong}
Intro: A  D   A   D   A   G   A  Asus2

Verse 1:
A   D         A     D  A       
My heart is empty
E     E        A    D
Your eyes are dull.
A     D       A      D  A
Once we were hungry,
G  D            A      A7
    Now we are full.

Chorus 1:
D      D7        A       D  A    
These ties that bind us,
B7                   D  Dsus4 D Dsus2
  Can't beat these chains.
A    D        A      D  A
 If  love is shelter,
G             D           A
   I'm gonna walk in the rain.

Bridge: D   A   D   A   G   A  Asus2

Verse 2:
A   D        A    D  A
You were my angel
E      E     A     D
Now you are real
   A    D   A     D  A
So like a stranger
G    D           A     A7
     Colder than steel

Chorus 2:
D     D7       A    D  A
The   morning after,
B7                  D  Dsus4  D  Dsus2
  You show what you bring
A    D         A          Asus2
 If  love is a red dress,
G         D           A
    Well, hang me in rags.






Bridge: D   A   D   A   G   A  Asus2

Chorus 3:
D   D7      A   D  A
Away___
E              E      A   Asus2
There goes the fairy tale.
D      D7         A    D  A
Lord, ain't it a shame?
D             A
In all this comfort,
G                A
I can't take the strain.

Bridge: D   A   D   A   G   A  Asus2

Verse 4:
A   D         A     D A
If  we played even
E     Esus4    A     D(sus4)
I'd  be your  queen
A       D         A        D A
But some-one was cheatin'
G     D         A   A7
  and it wasn't me

Chorus 4:
D   D7           A      D A
I played on the table
B7                   D  Dsus4 D Dsus2
  You held something back
A   D       A    D  A
 If love is aces
G  D           A
   Give me the jack

Outro: D   A   D   A   G   A
\end{lstsong}
\end{multicols}
\newpage

\begin{comment}

INTRO:
A    D  A    D  A    G   A   Asus2

VERSE 1:
A  D        A     D A
My heart is empty
E             A    D
Your eyes are dull
A    D       A      D A
Once we were hungry
G   D          A     A7
    Now we are full

CHORUS:
D               A        D A
These ties that bind us
B7                 D  Dsus4 D Dsus2
  Can't beat these chaaaaaains
A  D       A       D A
If love is shelter
G           D           A
  I'm gonna walk in the rain
D   A   D   A   G   A  Asus2

VERSE 2: [play like verse 1]
A   D     A    D  A
You were my angel
E          A     D
Now you are real
A    D      A    D A
So like a stranger
G    D      A   A7
     Colder than steel

CHORUS:
D           A     D A
The morning after
B7              D  Dsus4  D  Dsus2
  No one should braaaaaaaaaaaaag
A  D             A     Asus2
If love is a red dress
G      D          A
  Well hang me in rags
D   A   D   A   G   A   A7

BRIDGE:
D          A
Ooooooooh  well
E              Esus4 A    A7
There goes the fairy tale
D     Dsus4      A
Lord, ain't it a shame
D           A
In all this comfort
  G              A
I can't take the strain
D   A   D   A   G   A  Asus2


\end{comment}
