\songsection{I got stripes \hfill \normalfont Johnny Cash}
\noindent\rule{\columnwidth}{1pt}

\begin{lstsong}
Verse 1:
       C               G
On a Monday, I was arrested. 
                                    C
On a Tuesday, they locked me in the jail.
                               G
On a Wednesday, my trial was attested. 
                                                     C
On a Thursday they said guilty and the judge's gavel fell.
Chorus:
                                  G
I got stripes, stripes around my shoulders.
                                C
I got chains, chains around my feet.
                                   G
I got stripes, stripes around my shoulders,
                                                     C
and them chains them chains They're about to drag me down.
Verse 2:
     C                         G
On A Monday I Got My Stripe-ed Britches. 
                               C
On A Tuesday I Got My Ball And Chain
                                   G
On A Wednesday I'm Workin' Diggin' Ditches. 
                                                     C
On A Thursday Lord I Begged 'Em Not To Knock Me Down Again
Chorus: ...
                                                     C     D
and them chains them chains They're about to drag me down. (quick key change to D)
Verse 3:
      D                      A
On a Monday, my mama come to see me. 
                                    D
On a Tuesday, they caught me with a file.
                            A
On a Wednesday, I'm down in solitary. 
                                                D
On a Thursday, I start on bread and water for a while.
Chorus:
                                  A
I got stripes, stripes around my shoulders.
                                D
I got chains, chains around my feet.
                                   A
I got stripes, stripes around my shoulders,
                                                 D
and them chains them chains are about to drag me down.
\end{lstsong}
\newpage

