\songsection{I Wish, I Wish \hfill \normalfont Cat Stevens}
\noindent\rule{\columnwidth}{1pt}

\begin{multicols}{2}
\begin{lstsong}
Intro:
| C | Dm7 D7 | G | G7 F |
| C | Dm7 D7 | G | G7 F |

C          Dm7     D7     G      G7  F 
  I wish I knew, I wish I knew
C                Dm 
  What makes me, me, and what
D          G     G  F
makes you, you.
C            Dm     D        G     B
  It's just another point of view, ooo.
E            A7             D        B
  A state of mind I'm going through, yes.
E           A7           D     G      G  F
  So what I see is never true, ahhh.

C                Dm      D           G   G  F 
  I wish I could tell, I wish I could tell
C              Dm          D       G     G  F 
  What makes a heaven what makes a hell.
C          Dm     D       G     B
  And do I get to ring my bell, ooo.
E            A             D     B
  Or land up in some dusty cell, no.
E              A             D      G    G  F
  While others reach the big hotel, yeah.

Solo
| C | Dm D | G | G F |
| C | Dm D | G | G F |
| C | Dm D | G | G F |
| C | Dm D | G | G F |

C (break)                G       G  F 
  I wish I had, I wish I had
C               Dm            D        G G F 
  The secret of good, and the secret of bad.
C               Dm       D        G    B
  Why does this question drive me mad? ahhh.
E              A                 D    B
  'Cause I was taught when but a lad, yes,
E              A                 D    G  G F
  That bad was good and good was bad, ahhh.

C          Dm       D       G       G  F 
  I wish I knew the mystery of
C                   Dm
  That thing called hate,
         D            G       G  F 
and that thing called love.
C                Dm   D        G      B
  What makes the in-between so rough? ahhh.
E           A               D      B
  Why is it always push and shove? ahhh
E           A                D      G    G  F
  I guess I just don't know enough, yes.

Solo (vocals ad lib and fade)
| C | Dm D | G | G F |
| C | Dm D | G | G F |
| C | Dm D | G | G F |
| C | Dm D | G | G F |
\end{lstsong}
\end{multicols}
\newpage

\begin{comment}
Intro:  C Dm7 D7 G G7
 
C           Dm7       D7       G        G7
I wish I knew,  I wish I knew
C                       Dm7                  D7            G    G7
what makes me, me, and what makes you, you.
C             D7                    G       B
It's just another point of view, ooo.
E                 A7                     D         B
A state of mind I'm going through, yeah.
E               A7               D      G       F
So what I see is never true, nooo. 

C                  Dm7       D7             G       G7     
I wish I could tell, I wish I could tell
C                      Dm7              D7         G    G7
what makes a heaven what makes a hell.
C           D7                    G      B
And do I get to ring my bell, ooo.
E               A7                    D     B
Or land up in some dusty cell, nooo.
E                   A7                    D    G      F
While others reach the big hotel, yeah. 

Solo

C          Dm7     D7        G     G7
I wish I had, I wish I had
C                   Dm7                D            G       G7
the secret of good, and the secret of bad.
C                    D7                          G       B 
Why does this question drive me mad? why.
E                     A7                       D      B
'Cause I was taught when but a lad, yeah,
E                      A7                        D     G       F              
That bad was good and good was bad, nooo. 

C            Dm7        D7           G   G7
I wish I knew the mystery of
C                       Dm7                 D7              G       G7
that thing called hate, and that thing called love.
C                       D7                     G          B
What makes the in-between so rough? why.
E             A7                       D           B
Why is it always push and shove? why.
E             A7                         D      G        F   
I guess I just don't know enough, yeah.

Solo (fade out) 
\end{comment}

