\songsection{Lady Jane \hfill \normalfont Rolling Stones}
\noindent\rule{\columnwidth}{1pt}

\begin{lstsong}
   D          C                     G   D
My sweet Lady Jane, when I see you again
                C                   G   D
Your servant am I and will humbly remain
E7             Am
Just hear this plea my love
D7        G
On bended knees my love
C          D7           Am   Am D
I pledge myself to Lady Jane
 
   D         C                     G  D
My dear Lady Anne I've done what I can
               C                    G  D
I must take my leave for promised I am
E7           Am
This play is run my love
D7            G
Your time has come my love
C               D7            Am  Am D
I've pledged my troth to Lady Jane

D C G D C G D E7 Am D7 G C D7 Am  Am D

      D       C                  G  D
Oh my sweet Marie I wait at your ease
                   C                     G D
The sands have run out for your lady and me
E7         Am
Wedlock is nigh my love
D7            G
Her station's right my love
C         D7             Am   Am D    
Life is secure with Lady Jane
\end{lstsong}
\newpage


\begin{comment}
    D              C
     My sweet Lady Jane
                      G
     when I see you again
    D                C
     Yoyr servant am I
                        G   D
     And will humbly remain
    E7           Am
     Just heed this plea, my love
    D7           G
     On bended knees my love,
    C            D7           Am  D
     I pledge myself to Lady Jane.

     My dear Lady Anne
     I've done what I can.
     I must take my leave
     for promised I am.
     This play is run, my love.
     Your time has come my love.
     I've pledge my troth to Lady Jane.

Oh, my sweet Marie,
     I wait at your ease
     The sands have run out.
     For your Lady and me.
     Wedlock is nigh, my love,
     Her station's right, my love,
     Life is secure with Lady Jane.
\end{comment}

