\songsection{Ride on Baby \hfill \normalfont Rolling Stones}
\noindent\rule{\columnwidth}{1pt}

\begin{multicols}{2}
\begin{lstsong}
Besser in B

Intro: (Capo fifth fret for orig.) A E  A E

Verse 1:
A               E     F#m             A
A smile on your face, but not in your eyes.
D                      A   D                E
You're looking through me you don't feel it inside.

Chorus:
            A              F#m
Get out and ride on, baby, ride on, baby
A              F#m
ride on, baby, ride on, baby.

Verse 2:
        D                        E
I could pick your face out in an FBI file,
    D                     E
You may look pretty but I can't say the same
         A    E            A  E
for your mind      Ah, ah, ah.

Verse 3:
A              E  F#m             A
You walk up to me and try to look shy.
D                  A    D                  E
The red round your eyes says that you ain't a child.

Chorus

Verse 4:
           D                    E
Well, I've seen your face, in a trashy magazine.
    D                                    E
You know where you're going, but I don't like  
                  A    E            A  E       
the places you've been      Ah, ah, ah.


A E F#m A    D A D E


Chorus



Verse 5:
      D                           E
I can pick your face out from the front or behind.
    D                      E
You may look pretty, but I can't say the same
      A   E               A  E
for your mind.   Ah, ah, ah.

Verse 6: 
A             E    F#m       A
Laugh it up a bit. Give it a try.
D            A        D             E
If I'm not impressed, you can still cry.

Chorus

Verse 7:
       D                                    E
By the time you're thirty, gonna look sixty-five.
    D                           E
You won't look pretty, and your friends will have
               A  E
kissed you goodbye.

Chorus

Outro: (3x)
A              F#m
ride on, baby, ride on, baby.
\end{lstsong}
\end{multicols}
\newpage


