\songsection{Sweet Little Sixteen \hfill \normalfont Chuck Berry}
\noindent\rule{\columnwidth}{1pt}

\begin{multicols}{2}
\begin{lsttab}
Intro: (in Ab7)
E-8-8-6-6-4-4-3-3-1---|
B-9-9-7-7-6-6-5-5-2---|
G---------------------|
D---------------------|
A---------------------|
E---------------------|
\end{lsttab}
\begin{lstsong}
Chorus 1:
                         E
They're really rockin in boston
                  A
In pittsburgh, p.a.
                      E
Deep in the heart of texas
                        A
And round the frisco bay
              D
All over st. louis
                       A
Way down in new orleans
                   E
All the cats wanna dance with
                 A                 
Sweet little sixteen

Verse 1:
(Break)         E
Sweet little sixteen
(Break)              A
Shes just got to have
(Break)          E
About half a million
(Break)          A
Framed autographs
(Break)                  D
Her wallets filled with pictures
(Break)               A
She gets em one by one
(Break)        E
She gets so excited
(Break)                  A
Watch her look at her run








Bridge:
         D
Oh mommy mommy
             A
Please may I go
                        E
Its such a sight to see
                        A
Somebody steal the show
          D
Oh daddy daddy
             A
I beg of you
           E
Whisper to mommy
                      A
It's all right with you

Chorus 2:
Cause they'll be rockin on bandstand
In philadelphia p.a.
Deep in the heart of texas
And round the frisco bay
All over st. louis
Way down in new orleans
All the cats wanna dance with
Sweet little sixteen

Solo on Verse (Piano)

Chorus 2

Verse 2:
Sweet little sixteen
Shes got the grown up blues
Tight dress and lipstick
Shes sportin high heel shoes
Oh, but tomorrow morning
Shell have to chang her trend
And be sweet sixteen
And back in class again

Chorus 1
\end{lstsong}
\end{multicols}
\newpage

\begin{comment}
\begin{lsttab}
Rhytm through the whole song:
E-----------------|
B-----------------|
G-----------------|
D-----------------|
A-6-6-8-8-6-6-8-8-|
E-4-4-4-4-4-4-4-4-|
\end{lsttab}



Sweet Little Sixteen - Chuck Berry.

V1              
C                        G                         C
They're really rockin in Boston, in Pittsburgh, P. A.
                     G                           C
Deep in the heart of Texas and 'round the Frisco Bay.
             F                     C
All over St. Louis, way down in New Orleans,
                   G                        C
All the Cats wanna dance with, Sweet Little Sixteen.

V2
             G                          C
Sweet Little Sixteen, she's just got to have,
             G               C
about half a million, framed autographs.
                         F                             C
Her wallet's filled with pictures, she gets 'em one by one,
              G                             C
She gets so excited, watch her look at her run.

Chorus
            F                   C
Oh,  Mommy, Mommy, please may I go,
            G                                C
It's such a sight to see, somebody steal the show.
           F               C
Oh, Daddy, Daddy, I beg of you,
           G                          C
Whisper to Mommy, it's all right with you.

V3
C                          G                            C
Cause they'll be rockin on Bandstand, in Philadelphia P.A.,
                     G                           C
Deep in the heart of Texas and 'round the Frisco Bay.
             F                      C
All over St. Louis, way down in New Orleans,
                   G                        C
all the Cats wanna dance with, Sweet Little Sixteen.


Instrumental Chords of verse

Repeat V3

V4
             G                                C
Sweet Little Sixteen, she's got the grown up blues,
                G                                     C
Tight dress and lipstick, she’s sporting high heeled shoes.
                 F                             C
Oh, but tomorrow morning, she’ll have to change her trend,
              G                          C
And be sweet sixteen, and back in class again.

Repeat V3












SWEET LITTLE 16
written and performed by Chuck Berry

(verses and choruses follow same chord pattern)

CHORUS 1:
                          G       G7             C
They're really rockin' in Boston,   Pittsburgh, PA
                     G     G7                     C
Deep in the heart of Texas   and round the Frisco Bay
             F                        C
All over St. Louis, way down in New Orleans
                   G          G7              C
All the cats wanna dance with   Sweet Little 16

Verse 1:
Sweet Little 16, she's just got to have
About a half a million framed autographs
Her wallet's filled with pictures; she gets them one by one
Becomes so excited; won't you look at her run, boy?

Bridge:
           F                   C
"Oh Mommy, Mommy, please may I go?
                     G    G7
It's such a sight to see;   somebody steal the show
          F            C
Oh Daddy, Daddy, I beg you
           G     G7
Whisper to Mommy   it's all right with you"

CHORUS 2:
'Cause they'll be rockin' on the bandstand
Philadelphia, PA
Deep in the heart of Texas and round the Frisco Bay
All over St. Louis, way down in New Orleans
All the cats wanna dance with Sweet Little 16

(instrumental, same pattern as verses and choruses)

(chorus 2)

Verse 2:
Sweet Little 16, she's got the grownup blues
Tight dresses and lipstick
She's sportin' high-heeled shoes
Oh, but tomorrow mornin'
She'll have to change her trend
And be sweet 16 and back in class again

(chorus 1, with first line "But they'll be rockin' in Boston)

\end{comment}














