\songsection{Take A Chance On Me \hfill \normalfont ABBA}
\noindent\rule{\columnwidth}{1pt}

%Auch mit B F# C#m etc.

%\begin{multicols}{2}
\begin{lstsong}
Chorus:
N.C.                C
If you change your mind, I'm the first in line.
                                       G
Honey I'm still free, take a chance on me.
G
If you need me, let me know, gonna be around.
                                    C
If you've no place to go, if you're feelin down.
C
If your all alone when the pretty birds have flown,
                                       G
honey I'm still free, take a chance on me.

Gonna do my very best, and it aint no lie,
                                  C
if you put me to the test, if you let me try.

Bridge:
       Dm        G
Take a chance on me (that's all I ask of you),
       Dm        G
take a chance on me.

Verse 1:
Dm                                         C
We can go dancing, we can go walking, as long as were together.
Dm                                       C
Listen to some music, maby just talking, get to know you better.
                      Am                  F
cuz you know I've got so much I wanna do, when I dream I'm alone with you.
Am         F   G
It's magic.
Am                             F
You want me to leave it there, afraid of a love affair,
      Dm           G         Dm             G
but I think you know, that I can't let you go.

Chorus

Bridge

Verse 2:
           Dm
Oh you can take your time baby, I'm in no hurry.
  C                       Dm
I know I'm gonna get you. You don't want to hurt me,
                  C
baby don't worry, I aint gonna let you.
                     Am                       F
Let me tell you now, my love is strong enough to last
                            Am     F G
when things are rough. It's magic.
Am                            F
You say that I waste my time, but I cant get you off my mind.
     Dm           G         Dm       G
No I can't let you go, cuz I love you so.

Chorus
\end{lstsong}
\newpage

