\songsection{Too Much Love Will Kill You \hfill \normalfont Queen}
\noindent\rule{\columnwidth}{1pt}
\begin{multicols}{2}
\begin{lstsong}
Intro: |G D|C |G D|C |

             G             C             G
I'm just the pieces of the man I used to be
         Em               Bm/D             C
Too many bitter tears are raining down on me
    Am            Em
I'm far away from home
              Am           Em
And I've been facing this alone
             D9     D C
For much too long

            G           C                 G
I feel like no-one ever told the truth to me
      Em                  Bm/D              C 
About growing up & what a struggle it would be
      Am               Em
In my tangled state of mind
          Am              Em
I've been looking back to find
             D9     D C
Where I went wrong

G                  C
Too much love will kill you
       Em                 D
If you can't make up your mind
G                C
Torn between the lover
        Em             D
And the love you leave behind
G                 C
You're headed for disaster
          Em             D/A7
cause you never read the signs
G                  Cadd9
Too much love will kill you
      G    D C G D C
Every time









           G             C             G
I'm just a shadow of the man I used to be,
     Em                    Bm/D            C
& it seems like there's no way out of this for me.
  Am                Em
I used to bring you sunshine,
    Am         Em              D9     D C
now all I ever do is bring you down.

             G              C              G
How would it be if you were standing in my shoes?
          Em            Bm/D          C 
Can't you see that it's impossible to choose?
    Am                Em
No, there's no making sense of it,
  Am              Em       D9     D C
ev'ry way I go, I have to  loose, oh

G                  C
Too much love will kill you
        Em             D
just as sure as non at all.
      G                         C
It'll drain the power that's in you,
         Em                   D
make you plead and scream and crawl.
        G                  C
And the pain will make you crazy,
           Em             D/A7
you're the victim of your crime:
G                  Cadd9           G
Too much love will kill you, every time.

G                  C
Too much love will kill 
      Em              D
It'll make you life a lie
     G                  C
Yes, too much love will kill you
        Em               D
And you won't understand why
       G                      C
You'll give your life, you'll sell your soul
    Em            D/A7
but here it comes again
G                  Cadd9            G
Too much love will kill you, in the end.
\end{lstsong}
\end{multicols}
\newpage

\begin{comment}
\songsection{Too Much Love Will Kill You \hfill \normalfont Queen}
\begin{songs}{}\beginsong{}

\beginverse
%\nolyrics Intro: \[G] \[D/G] \[C/G] \[G] \[D/G]
\nolyrics Intro: \[G] \[D] \[C] \[G] \[D] \[C]
\endverse

\beginverse\memorize
\[C/E] \[D4] I'm just the \[G]pieces of the \[C7+]man I \[C]used to \[G]be
D/G Em Bm C
Toa many b'tter tears are raining dawn an ine
Am Em Am Em
I'm far away from home, and I' ve been facing this alone
D11 D C9
for much oa 'cng.
told
everthe true a me,
I feei 'ike no 'one
D" i Em Btn C
'bout groiwi.ng' up and what a struggie ='- would be.
Am Em Arri
In my ' angled state of mind, Irve been looking back to
Em D1' D C9
find where I went. wrong
Refrain
G Em D
Toa much lave iwf il kili you ' f yau csn't make up you
G C Em
tom between -'he lover, and the .1.ove you 'eave beh
G/B C G/D Ck7
You'
headed for disast:er, cause you never read the signs,
re
G/D C/D G
Tao mucln love wi' ' k' ll yau every time
\endverse

\beginverse
2. I'm just a shadow af the man used to be,
and it seems like there's no way out of t.h"'s far me.
I used to
bring yau sunshi.ne
nolw a
ever do is br ng you down.
Haw wau'd ' t be if yau were standing rn mv shoesy
see it's impossib'e ta cnaosey
Can't you
ffo there's na mak.'ng sense af it,
ev'xy way I co i have ta lose, ch
Tao much, iovc wil' kill yau just ss s tre as nan at. all.
't''1 drain the power that's in yau,
make yott plead snd screani. and crawl
crime,
the
re the pa'n wir.'
Aridvrctzm o your make you crazy, you'
Toaki' ' you
t:me.
every
wiil
love much
'oa much lave w:ll kil' vou l t will make your 1' fe a lie,
yes tao much iove wil' k'I' yau, snd you wcn't understand why.
you'll give your ii. e yau' ll send yaur soul, but. he.re it comes again,

\endverse

\endsong
\end{songs}
\end{comment}


