\songsection{With A Little Help From My Friends \hfill \normalfont Beatles}
\noindent\rule{\columnwidth}{1pt}
\begin{lstsong}
Verse 1
C              G          Dm
What would you think if I sang out of tune
                       G7          C
Would you stand up and walk out on me?
C            G             Dm
Lend me your ears and I'll sing you a song
                    G7          C
And I'll try not to sing out of key

Chorus:
         Bb               F            C
Oh I get by with a little help from my friends
         Bb                 F            C
Mm I get high with a little help from my friends
         Bb                F            C         G7
Mm gonna try with a little help from my friends

Verse 2:
C         G          Dm
What do I do when my love is away?
                  G7     C
Does it worry you to be alone?
C        G           Dm
How do I feel by the end of the day?
                           G7      C
Are you sad because you're on your own? No..

Chorus

Bridge:
C      Am7     D7      C        Bb      F
Do you need anybody? I need somebody to love
(C)      Am7   D7      C        Bb      F
Could it be anybody? I want somebody to love

Verse 3:
C           G          Dm
Would you believe in a love at first sight?
                        G7              C
Yes I'm certain that it happens all the time
C           G            Dm
What do you see when you turn out the light?
                        G7        C
I can't tell you, but I know it's mine

Chorus
Bridge
Chorus
\end{lstsong}
\newpage

\begin{comment}
Outro:
          Bb               F            C

Yes I get by with a little help from my friends
                           Bb       F         C
With a little help from my frieeeeeeeeeeds my friends.
\end{comment}

